Denotational Semantics for SSA with Weak Memory Operations

### 2023-10-10 pldi24/paper.tex
Added more stubs

@@

\TODO{metatheory: substitution, rewriting, etc}
\TODO{\(\implies\) E-graph optimization}

@@

\TODO{Ye Olde State Transformer}

@@

@@

\TODO{Pomsets}

\TODO{SC Monad}

\TODO{Building The Weak Memory Monad}

>>>>

\begin{figure}
  \TODO{this}
  \caption{Typing rules for \isotopessa substitutions}
  \Description{Typing rules for isotope-SSA substitutions}
  \label{fig:ssa-block-typing}
\end{figure}

\begin{theorem}[Substitution] \
  \TODO{this}
\end{theorem}

@@

\begin{theorem}[Semantic Substitution] \
  \TODO{this}
\end{theorem}

\TODO{\(\implies\) E-graph optimization}

\begin{figure}
  \begin{center}
    \TODO{this}
  \end{center}
  \caption{Grammar for \isotopessa expressions with holes}
  \Description{Grammar for isotope-SSA expressions with holes}
  \label{fig:ssa-semantics}
\end{figure}

\begin{theorem}[Rewriting] \
  \TODO{this}
\end{theorem}

@@

\TODO{Is Elgot}

@@

\TODO{Is Elgot}

\TODO{Ye Olde Reader/Writer/State Transformer}

@@

\TODO{Pomsets...}

\TODO{Form a monoid, so we can define...}

\TODO{The SC Monad, which, via composition w/ the state transformer, lets us}

\TODO{Build The Weak Memory Monad, which is too powerful, so we do...}
